### 2023-11-22 ms.qmd
Updates

```{r, models1}
#| label: models1
#| echo: false
#| warning: false

# Generalized Mixed Models delicata
GMM_deli <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
summary(GMM_deli)

emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
emmeans(GMM_deli, pairwise ~ cort*Associative_Trial)

# Generalized Mixed Models guichenoti
GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"))
summary(GMM_guich)

emmeans(GMM_guich, pairwise ~ temp*Associative_Trial)
emmeans(GMM_guich, pairwise ~ cort*Associative_Trial)
emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)

>>>>

```{r, models1}
#| label: models1
#| echo: false
#| warning: false
library(emmeans)
library(lme4)
# Generalized Mixed Models delicata
GMM_deli <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
summary(GMM_deli)
emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
emmeans(GMM_deli, pairwise ~ cort*temp*Associative_Trial)

# Generalized Mixed Models guichenoti
GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"), control = glmerControl(maxit = 1000))
summary(GMM_guich)

emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)

# Generalized Mixed Models delicata REVERSAL
GMM_deli_rev <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = binomial(link = "logit"))
summary(GMM_deli)

emmeans(GMM_deli_rev, pairwise ~ cort*temp*trial_reversal)
emmeans(GMM_deli_rev, pairwise ~ temp*trial_reversal)

# Generalized Mixed Models guichenoti REVERSAL
MM_guich <- glmer(FC_reversal ~ trial_reversal*temp*cort + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = binomial(link = "logit"))
summary(GMM_guich)

emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)
```

```{r, models2}
```
